Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Fix figure reference

## Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
We tie the constructs of lexical, interlocutor, and social/physical cohesion
together in a theoretical framework called sociolinguistic cohesion, as shown in
Figure X. We can measure the changes in cohesion preceding and in response to
external stimuli by evaluating the messages and the context in which they occur.
Several mechanisms are in motion here. Previous values of linguistic cohesion
should influence future values of linguistic cohesion. They should also
influence future actions in the real world space. Previous events influence
future events, and also the future cohesiveness of the opposition.

>>>>

## Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
We tie the constructs of lexical, interlocutor, and social/physical cohesion
together in a theoretical framework called sociolinguistic cohesion, as shown in
Figure \@ref(fig:theoretical-framework). We can measure the changes in cohesion
preceding and in response to external stimuli by evaluating the messages and the
context in which they occur. Several mechanisms are in motion here. Previous
values of linguistic cohesion should influence future values of linguistic
cohesion. They should also influence future actions in the real world space.
Previous events influence future events, and also the future cohesiveness of the
opposition.
